Two Problems for Sophistication

### 2015-01-21 Facticity/Facticity/paper.tex
...

\begin{proof}
Note that since $\phi_i$ is a prefix function, if $\phi_i$ is defined for input $\epsilon$ then it cannot be defined for any other input. Pick $i,x$ with $\phi_i(\epsilon)=x$. Note that $x$ can be computed from $i$ and a fixed program, so there is a $c$ such that $C^{\K, \phi}(x)\le C^{\K, \phi}(\phi_i)+c$. Vice versa, given any $x$ we can construct an index of $f$, since $\psi$ is an acceptable numbering. Therefore $|K(f)-K(x)|\le c$.

We now define a computable function $D$ by $D(\bar\imath p)=j$ where $\psi_j(\epsilon) = \psi_i(p)$.  We will show that the two conditions of Lemma~\ref{lemma:thecoolone} hold for the prefix function $D$.

@@

We first show that representions using $\T$ can be reduced to representations in $\F$ with a small overhead.

>>>>

\begin{proof}
Let $\phi_i$ be a singleton for $x$ as described. Note that since $\phi_i$ is a prefix function, if $\phi_i$ is defined for input $\epsilon$ then it cannot be defined for any other input. Pick $i,x$ with $\phi_i(\epsilon)=x$. Note that $x$ can be computed from $i$ and a fixed program, so there is a $c$ such that $C^{\K, \phi}(x)\le C^{\K, \phi}(\phi_i)+c$. Vice versa, given any $x$ we can construct an index of $\phi_i$, since $\phi$ is an acceptable numbering. Therefore $|C^{\K,\phi}(\phi_i)-C^{\K, \phi}(x)|\le c$.

We now define a computable function $D$ by $D(\bar\imath y)=j$ where $\psi_j(\epsilon) = \psi_i(y)$.  We will show that the two conditions of Lemma~\ref{lemma:thecoolone} hold for the prefix function $D$.

@@

We first show that representations using $\T$ can be reduced to representations in $\F$ with a small overhead.
